\documentclass[12pt,a4paper]{report}  

 \begin{document}  
 \paragraph{}
 For a successful team, effective and efficient communication is necessary. And some constructive conflicts are also good for the project. However, same as most teams, at the beginning, our team encountered a series of communication problems as well. First of all, although meetings are a good way to share ideas and proposals, we often have different ideas and opinions with our powerful personalities. As a result, some personal ideas are hard to be expressed easily, which would otherwise bring promising outcome. As we talk about the database which we will use, some of us suggest MySQL but the others are Mango DB. At the end, we have investigated a lot of information about the database which lead us to unified opinion. In addition, after we evaluated the old system. Some of us prefer to improve the previous one but the others prefer to create a new one. At this time when we don?t know which one is better, our supervisor gave us a good approach to negotiate with our stakeholder to provide us a new project. Moreover, some common issues about jobs assignment also happen to us. We have to write the interim report and coding for first version of our application at the same time. Therefore, some of us think we should work on one task together and the other idea is to split up our team into two small group and each group do one mission. Meeting face to face is always a good way to solve problems. We discussed the problem face to face and solved it which is split up into two group. This method can make us focus on only one task and to finish it better and easier.  \end{document}